\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-13 doc/sui14/iteration2.tex
grammar grammar

\sean{If possible, add how we observed participants physical movements in this iteration. Better if we can compare to i1.} One side effect that we have observed in this approach is that the {\em Intensity IR} sometimes eliminates the desired target during the {\em scanning} stage. Out of 300 trials, 13 of them (4.3\%) has been accidentally eliminated. This is higher than the error rate for {\em Naive IR} (only 5 out of 300, ~1.6\%). \changes{Even though the higher error rate increases the chance of multiple attempts in target selection, from our analysis above which has included the error trials, we see that the overall performance of {\em Intensity IR} is still better than {\em Naive IR}. }  % but this is the trade-off for the overall faster acquisition time.

>>>>

\sean{If possible, add how we observed participants physical movements in this iteration. Better if we can compare to i1.} One side effect that we have observed in this approach is that the {\em Intensity IR} sometimes eliminates the desired target during the {\em scanning} stage. Out of 300 trials, \changes{the target is accidentally eliminated in 13 (4.3\%).} This is higher than the error rate for {\em Naive IR} (5 out of 300, ~1.6\%). \changes{Even though the higher error rate increases the chance of multiple attempts in target selection, our analysis above illustrates that overall performance of {\em Intensity IR} is still better than {\em Naive IR}. }  % but this is the trade-off for the overall faster acquisition time.
